Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-02-05 paper.tex
Intro

Generally, embedded computer systems perform dedicated functions with a high degree of reliability. They are used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers~\cite{Kopetz11}. Embedded systems are ubiquitous in modern day information systems and are also becoming increasingly important in our society, especially in micro-grids, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}, in multipurpose mobile devices, which now help in performing many routine daily tasks, and in cyber-physical systems (CPS), which demand short development cycles and again high levels of reliability~\cite{leeCPS,leeCPS2}. As a consequence, human life has also become more and more dependent on services provided by this type of system and, in particular, their success is strictly related to both service relevance and quality/reliability.

>>>>

Generally, embedded computer systems perform dedicated functions with a high degree of reliability. Embedded systems are ubiquitous in modern day information systems and are also becoming increasingly important in our society, and nowadays, they are employed to process, monitor, and control every human activity: factories, power plants, mobile devices, robotics, traffic control, vehicles, and home appliances. They are used in a variety of sophisticated applications, which range from entertainment software, such as games and graphics animation, to safety-critical systems, such as nuclear reactors and automotive controllers~\cite{Kopetz11}. Naturally, the interaction between embedded softwares and physical processes created a different class of systems with a mixture of continuous and discrete dynamics, {\it i.e.} hybrid systems. The domain of embedded systems allied to the most recent communication revolution cause an intense integration between different and spread physical processes (that are usually embedded systems) and computation. Those complex, hybrid and integrated systems are called cyber-physical systems (CPS).

The main difference between embedded systems and CPS is indeed the strong presence of modern communication technologies ({\it e.g.}, Internet of Things) in the last ones. This simple difference causes a revolution in terms of flexibility, scalability, and complexity of hybrid systems so-called CPS and adds a novel class of problems to the already known challenges of embedded systems. For example, micro-grids,{\it i.e.} small-scale electricity systems that groups different sources of distributed generation (DG) and loads, are emerging CPS's, where reliability and carbon emission reduction are of paramount importance~\cite{xu15}. Note that, each DG and the majority of loads already employed embedded softwares and present several safety-critical requirements, however the integration of them constitute a CPS where arises additional challenges related to synchronism, stability, control, communication, and reliability  of entire micro-grid.

Thus CPS's demand short development cycles and high levels of reliability and robustness~\cite{leeCPS,leeCPS2} and present challenges that include but is not limited to the the the embedded system challenges.  As a consequence of the popularization, human life has also become more and more dependent on services provided by this type of system and, in particular, their success is strictly related to both service relevance and quality/reliability.
